Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-05 journal paper/itcs18paper/app-examples.tex
Minor edit.
Removed some coloring.

We consider Bayesian MAB with Bernoulli rewards. There are $T$ rounds and $K$ arms. In each round $t\in [T]$, the algorithm chooses an arm $a_t\in A$ and receives a reward $r_t\in\{0,1\}$ for this arm, drawn from a fixed but unknown distribution. The set of all arms is $A$; mean reward of arm $a$ is denoted $\mu_a$. \asedit{The mean reward vector $\mu = (\mu_a:\; a\in A)$ is drawn from a common Bayesian prior $\priorMu$.}
We let
    $\rew(t) = \mu_{a_t}$
denote the instantaneous mean reward of the algorithm.

@@

\begin{theorem}[\citet{Selke-BE-2020}]\label{thm:TS-mono}
\asedit{Assume the prior $\priorMu$ is independent across arms.} Then \Thompson is \bmonotone. Consequently, it satisfies $\BIR(t)\leq \tildeO(t^{-1/2})$.
\end{theorem}

The theorem follows easily from two observations in  \citet{Selke-BE-2020}, we provide the proof for completeness. First, let us state the algorithm. Let $\Pr^t$ and $\E^t$ denote, resp., Bayesian posterior probability and expectation conditional on the history observed at time $t$. Let $a^*$ be the best arm: $a^*\in \argmax_a \mu_a$. In each round $t$, \Thompson samples arm $a_t$ as follows:
\begin{align}\label{eq:TS-defn}
    \Pr[a_t=a] := {\Pr}^t[a^*=a]
    \quad\text{for each arm $a$}.
\end{align}
\swcomment{do we want to say $\Pr$ is over sampling first from prior and then generate history?}

>>>>

We consider Bayesian MAB with Bernoulli rewards. There are $T$ rounds and $K$ arms. In each round $t\in [T]$, the algorithm chooses an arm $a_t\in A$ and receives a reward $r_t\in\{0,1\}$ for this arm, drawn from a fixed but unknown distribution. The set of all arms is $A$; mean reward of arm $a$ is denoted $\mu_a$. The mean reward vector $\mu = (\mu_a:\; a\in A)$ is drawn from a common Bayesian prior $\priorMu$.
We let
    $\rew(t) = \mu_{a_t}$
denote the instantaneous mean reward of the algorithm.

@@

\begin{theorem}[\citet{Selke-BE-2020}]\label{thm:TS-mono}
Assume the prior $\priorMu$ is independent across arms. Then \Thompson is \bmonotone. Consequently, it satisfies $\BIR(t)\leq \tildeO(t^{-1/2})$.
\end{theorem}

The theorem follows easily from two observations in  \citet{Selke-BE-2020}, we provide the proof for completeness. First, let us state the algorithm. Let $\Pr^t$ and $\E^t$ denote, resp., Bayesian posterior probability and expectation conditional on the history observed at time $t$. Let $a^*$ be the best arm: $a^*\in \argmax_a \mu_a$. In each round $t$, \Thompson samples arm $a_t$ from the posterior distribution $p_t(a) = {\Pr}^t[a^*=a]$.
